Thoughts on resubmission within ARC1

### 2009-02-13 doc/client/client_technical.tex
spell checking, format modifications etc

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Mattias Ellert, Bjarte Mohn, Ivan Marton, Gabor Roczei},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\arclib}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large {\arclib}}\Large \par}
\vspace*{0.5cm}

@@

\begin{itemize}
\item{handling proxy, user and host certificates,}
\item{performing resource discovery and information retrieval,}
\item{job submission and management and}
\item{data handling.}
\end{itemize}

@@

The new {\arclib} makes extensive use of plugins for command
handling. These plugins are handled by a set of higher level classes
which thus are the ones to offer the plugin functionality to external
calls. In this section an overview of the library's main functionality
is given which also introduces the most important higher level
classes.

@@

With the increasing number of grid clusters around the world, a
reliable and fast resource discovery and information retrieval
capability is of crucial importance for a user interface. The new
{\arclib} resource discovery and information retrieval component
consists of three classes; the {\TargetGenerator}, the
{\TargetRetriever} and the {\ExecutionTarget}. Of these the
{\TargetRetriever} is a base class for further grid middleware
specific specialization (plugin).

@@

\begin{enumerate}
\item{The {\TargetGenerator} has prepared a list of
  {\ExecutionTarget}s. Depending on the {\URL}s provided to the
  {\TargetGenerator} the list of found {\ExecutionTarget}s may be
  empty or contain several targets. Targets may even represent more
  than one grid flavour. The list of found targets are given as input
  to the {\Broker}.}
\item{In order to rank the found services ({\ExecutionTarget}s) the
  {\Broker} needs detailed knowledge about the job requirements, thus
  the {\JobDescription} is passed as input to the brokering process.}
\item{The {\Broker} outputs a ordered list of {\ExecutionTarget}s
  according to the provided {\JobDescription}.}
\item{Each {\ExecutionTarget} has a method to return a specialized
  {\Submitter} which is capable of submitting jobs to the service it
  represents. The best suitable {\ExecutionTarget} for the job is
  asked to return a {\Submitter} for job submission.}
\item{The {\Submitter} takes the {\JobDescription} as input and
  uploads it to the computing service.}
\item{The {\Submitter} identifies local input files from the
  {\JobDescription} and uploads them to the computing service.}
\end{enumerate}

@@

Once a job is submitted job related information (job identification
string, cluster etc) is stored in a local XML file which hosts similar
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

\begin{enumerate}
\item{The {\JobSupervisor} takes four arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second is a list of strings containing job identifiers and job
  names, the third is a list of strings of clusters to select or
  reject (in the same format as described for the {\TargetGenerator}
  above). The last argument is the name of the file containing the
  local information about active jobs, hereafter called the joblist
  file.}
\item{A job identifier does not uniquely define which grid flavour
  runs a certain job. Thus this information is stored in the joblist
  file upon submission by the {\Submitter} and the joblist file is
  extensively used by the {\JobSupervisor} to identify the
  {\JobController} flavours which are to be loaded. The information in
  the joblist file is also used to look up the job identifier for jobs
  specified using job names. Alias resolution for the selected and
  rejected clusters are performed using the information in the
  {\UserConfig} object.}
\item{Suitable {\JobController}s are loaded}
\item{The list of job identifiers and selected and rejected clusters
  are passed to each {\JobController} which uses the information to
  fill its internal \texttt{JobStore}.}
\item{Residing within the {\JobSupervisor} the {\JobController}s are
  now accessible for external calls (i.e. job handling).}
\end{enumerate}

@@

In this section an overview of all important classes in the new
{\arclib} is given. The overview is subdivided in two parts where
first all the generic classes are presented,
Section~\ref{sec:genclass}, before the grid flavour specializations
are presented in Section~\ref{sec:plugins}. Classes are described both
in words and by code.

@@

The {\ExecutionTarget} is the class representation of a computing
resource (queue) capable of executing a grid job. It serves as input
to the {\Broker} which is foreseen to be able to select between
different {\ExecutionTarget}s from different grid flavours without a
priori knowing their difference. The {\ExecutionTarget} class mimics
the Glue2 information model (with a flattened structure), and thus a
mapping between attributes from other information systems into the
Glue2 format is needed. Appendix \ref{app:ExTarget} shows the current
mapping for the production ARC, ARC1 and gLite middlewares.

@@

Following a broker decision jobs are to be submitted. Since all
information about the selected computing service resides within the
selected {\ExecutionTarget}, the {\ExecutionTarget} is capable of
returning a {\Submitter} capable of submitting a job to the service it
represents.

@@

The Broker inherits from the {\ACC} base class in order to be loadable by the ARC \texttt{Loader}. It is the base class of the specialized Brokers. If you are using command arcsub then you can choose a broker type with with ``-b`` parameter. There is a solution for adding parameters to these descendants Brokers. Here is an example:

\begin{shaded}
\begin{verbatim}
arcsub -b RandomBroker:a,b,c -c ARC1:https://knowarc1.grid.niif.hu:60000/arex job.jsdl
\end{verbatim}
\end{shaded}

The Broker's constructor sets the PreFilteringDone and the TargetSortingDone values to false because we need to call the PreFilterTargets first then the second the GetBestTarget which triggers the specialised Broker sorting method.

The base Broker operations are the followings:

\begin{enumerate}
\item{The first step is the PreFilterTargets, this implements the matchmaking: the JobDescription and the TargetGenerator's ExecutionTargets will be compared inside this method. JobDescription encapsulate the job's JobInnerRepresentation, and the ExecutionTarget involves the candidate cluster's queue information. There are main elements in the JobInnerRepresentation which are used for matchmaking, these are documented in  Appendix: \ref{sec:broker-mapping}, all matchmaking elements and their comparison logic are there. The macthmaking works the following way: it takes every JobInnerrepresentation elements which are relevant and  check them in an ordered way. If a matchmaking element is not presented in the JobInnerRepresentation then it will be ignored, but if it is there than the ExecutionTarget should compare. For example SessionLifeTime is in the JobInnerRepresentaion and the WorkingAreaLifeTime is in the ExecutionTarget (these are matchmaking pair). If the WorkingAreaLifeTime is not defined then the Broker cannot check the times therefore it will ignore this cluster, but if the WorkingAreaLifeTime exist and the comparison between this elements are true then this check will be passed otherwise the cluster will be ignored. We are using this rule for checking every elements. There is only one exception that is the ProcessingStartTime. If the DownTime is not defined in the ExecutionTarget than we can believe it that the job can start anytime and it will not be killed by shutdown. This rule checking runs for every ExecutionTargets and if every matchmaking checks are successfull for a target then this ExecutionTarget will be added to the PossibleTargets vector.}
\item{When the matchmaking has finished then  the PreFilteringDone variable will be set to true and the TargetSortingDone will be set to false. }
\item{The next step is calling the GetBestTarget method, which will give an ExecutionTarget candidate. If the PossibleTargets vector is empty then it will give nothing. The GetBestTarget will call the specialid Broker type sorting  method. This SortTargets method is a virtual method, therefore every specialised Broker should implement it.}
\item{When the SortTargets has finished then the TargetSortingDone will be true and the GetBestTarget will return the first element of the PossibleTargetVector and the current iterator will be incremented by one.}
\item{If the submision fails to this cluster then we can call the GetBestTarget again and we will get an other ExecutionTarget till it will not consumes. If  the targets run out from the PossibleTargetVector then the GetBestTarget's boolean parameter (EndOfList) will be true}
\end{enumerate}

\begin{shaded}
\begin{verbatim}
class Broker : public ACC {
public:
    ExecutionTarget& GetBestTarget(bool &EndOfList);
    void PreFilterTargets(Arc::TargetGenerator& targen, Arc::JobDescription jd);    
protected:
    Broker(Config *cfg);
    virtual ~Broker();
    virtual void SortTargets() = 0;
    std::vector<Arc::ExecutionTarget> PossibleTargets;
    bool TargetSortingDone;
    Arc::JobInnerRepresentation jir;
    static Logger logger;
private:
    std::vector<Arc::ExecutionTarget>::iterator current;
    bool PreFilteringDone;
};
\end{verbatim}
\end{shaded}

The Broker class encasulated two useful data elements: logger and JobInnerRepresentation. These can be helpful when somebody creates a specialised Broker and wants to use the logger and needs some information about the job.

@@

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\arclib} library this functionality is implemented in the
{\JobDescription} class. The inner representation (\texttt{JobInnerRepresentation}
class) is similar to the GIN-JSDL and all elements correspond to
variables. These variables are either simple variables or complex data structures,
and are private in the {\JobDescription} class.

This is a generic class that takes a job
description (string) as input

@@

in any supported formats (currently XRSL~\cite{xrsl}, JDL~\cite{jdl},
JSDL~\cite{jsdl}), converts and stores it in a GIN-JSDL-like internal job
description format. The identification of the source description
format is internally handled by a \texttt{JobDescriptionOrderer} class
which identifies the format by pattern matching. If the source string is
empty or the \texttt{JobDescriptionOrderer} class can not be recognized
to any formats, then it does not store anything and returns with false, otherwise
it converts and stores it.

Different operations, like getting the job description in other
formats or getting job-related information, can be performed by using the
description-independent functions of this class, e.g.:

@@

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern matching
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.
If the inner representation is empty or the source job descrition is not
valid, then the output is empty too and returns with false.
When the source format is the same as the output format and it is not XRSL,
than we set the product string to the source string. The XRSL output is
always generated from the inner representation.

Parsing is currently possible from any of the languages. JSDL, XRSL and
JDL output generation is implemented already but even for these there are
some limitations.

The conversion mainly means a syntactical transformation and the
{\JobDescription} class can do nothing in those cases where
there are not enough data is available to assemble a given attribute or
when information can be lost because the received attribute has no
equivalent in the output language.

@@

The {\Job} is a generic job class for storing all job related
information. Attributes are derived from the Glue2 information model
and thus a mapping is needed for non Glue2 compliant grid middlewares.
Appendix \ref{app:job} shows the present mapping schema.

@@

The gLite computing element offers several interfaces, one of them
being the Web Service based computing element interface known as the
CREAM CE~\cite{cream}. The current revision of this interface (CREAM
version 2) has been chosen for implementation within {\arclib} for the
following reasons:

@@

\subsection{Broker plugins}

\subsubsection{RandomBroker}

The ExecutionTarget sorting is based on randomization, the PossibleTargets vector will be shuffled.

\subsubsection{FastestCPUBroker}

The sorting method is based on the fastest CPU, we use the CINT2000 (Integer Component of SPEC CPU2000) benchmark for this purpose , here are more information about this benchmark type:

http://www.spec.org/cpu2000/CINT2000/

The sorting algorithm for this Broker is as follows:

\begin{enumerate}
\item{There is a cluster filtering at the begining of the sorting. If the cluster is not publish the specint2000 benchmark information then it will be ignored.}
\item{The cluster having the highest specint2000 value will be the first in the PossibleTargets vector which has }
\end{enumerate}

\subsubsection{FastestQueueBroker}

The sorting method is based on the shortest queue, where the number waiting jobs  of  is the lowest.

The sorting algorithm for this Broker is as follows:

\begin{enumerate}
\item{The clusters which do not involve the target sorting information will be removed  (WaitingJobs, TotalSlots and FreeSlots).}
\item{Sort the targets according to the number of waiting jobs (in percent of the cluster size). The cluster will be better where the WaitingJobs number divided by the TotalSlots gives the lower number. This solution will result that the scale queue will be independent from the cluster size.}
\item{If several clusters(queues) have free slots (CPUs) do basic load balancing}
\end{enumerate}

\subsubsection{DataBroker}

The main idea was that the jobs should submit to that cluster where the data is. The sorting method is based on the A-REX file cache checking. There is a CacheCheck interface inside the A-REX which can be used to query whether files in question are present or not in the cache directory. There is a limitation at the current state because the CacheCheck interface can only use this cache directory format:

@@

If the cachedir parameter involves {\%}U or other substitute element then the CacheCheck will not work.

The sorting algorithm for this Broker is as follows:

\begin{enumerate}
\item{Only the A-REX service has CacheCheck method therefore the other clusters will be ignored}
\item{The URL files are collected from the JobInnerRepresentation }
\item{All of the ExecutionTargets which are A-REXs will be called by their  CacheCheck method. Single query used for achieving all the necessary information. The Broker will summarize the file sizes. The CacheMappingTable is an array where the A-REX's URL is the key and the summarized file size is the value. When there is some problem to query file size from the A-REX then the summarized size will be zero.}
\item{The last step is to sort the PossibleTargets vector in descending order  (CacheMappingTable used for this), which cluster having the most data that will be at the front of the vector.}
\end{enumerate}

Example for CacheCheck request what can be sent to an A-REX service:

@@

Example CacheCheck response of the A-REX service:

@@

\subsubsection{PythonBroker}

This broker allows users to write their customized broker in
python. To use this broker the user should write a python class. The
class should contain:

@@

The Config, ExecutionTarget and JobInnerRepresentation classes are
available in the swig generated arc python module.

To invoke the python broker, the name of the python module defining
the broker class and the name of the broker class must be given. If
e.g. the broker class MyBroker is defined in the python module
SampleBroker the command line option to arcsub to use this broker is:

@@

Given all components listed above it is possible to write versatile
command line interfaces (cli) for grid job submission and
management. {\arclib} offers the following native commands:

@@

\section{Domain and Location attributes}

\subsection*{std::string DomainName}

ARC0: nordugrid-cluster-name \\
CREAM: GlueSiteName

\subsection*{std::string Owner}

ARC0: nordugrid-cluster-owner

\subsection*{std::string Address}

\subsection*{std::string Place}

CREAM: GlueSiteLocation

\subsection*{std::string PostCode}

ARC0: nordugrid-cluster-location

\subsection*{float Latitude}

CREAM: GlueSiteLatitude

\subsection*{float Longitude}

CREAM: GlueSiteLongitude

\section{ComputingService and ComputingEndpoint attributes}

\subsection*{std::string CEID}

\subsection*{std::string CEName}

\subsection*{std::string Capability}

\subsection*{std::string Type}

\subsection*{std::string QualityLevel}

\subsection*{URL url}

ARC0: nordugrid-cluster-contactstring \\
CREAM: GlueCEInfoContactString

\subsection*{std::string Technology}

\subsection*{std::string Interface}

ARC0: ``GridFTP''

\subsection*{std::string InterfaceExtension}

\subsection*{std::string SupportedProfile}

\subsection*{std::string Implementor}

ARC0: ``NorduGrid''

\subsection*{std::string ImplementationName}

ARC0: ``ARC0'' \\
CREAM: GlueCEImplementationName

\subsection*{std::string ImplementationVersion}

ARC0: nordugrid-cluster-middleware \\
CREAM: GlueCEImplementaionVersion

\subsection*{std::string HealthState}

ARC0: nordugrid-queue-status

\subsection*{std::string ServingState}

CREAM: GlueCEStateStatus (GlueVOView $||$ GlueCE)

>>>>

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Mattias Ellert, Bjarte Mohn, Ivan Marton, Gabor Roczei},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\RandomBroker}{\texttt{RandomBroker}}
\newcommand{\FastestCPUBroker}{\texttt{FastestCPUBroker}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\DataBroker}{\texttt{DataBroker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large {\libarcclient}}\Large \par}
\vspace*{0.5cm}

@@

\begin{itemize}
\item{handling proxy, user and host certificates,}
\item{performing resource discovery and information retrieval,}
\item{filtering and brokering of found resources,}
\item{job submission and management and}
\item{data handling.}
\end{itemize}

@@

The new {\libarcclient} makes extensive use of plugins for command
handling. These plugins are handled by a set of higher level classes
which thus are the ones to offer the plugin functionality to external
calls. In this section an overview of the library's main functionality
is given which also introduces the most important higher level
classes.

@@

With the increasing number of grid clusters around the world, a
reliable and fast resource discovery and information retrieval
capability is of crucial importance for a user interface. The new
{\libarcclient} resource discovery and information retrieval component
consists of three classes; the {\TargetGenerator}, the
{\TargetRetriever} and the {\ExecutionTarget}. Of these the
{\TargetRetriever} is a base class for further grid middleware
specific specialization (plugin).

@@

\begin{enumerate}
\item{The {\TargetGenerator} has prepared a list of
  {\ExecutionTarget}s. Depending on the {\URL}s provided to the
  {\TargetGenerator} the list of found {\ExecutionTarget}s may be
  empty or contain several targets. Targets may even represent more
  than one grid flavour. The list of found targets are given as input
  to the {\Broker}.}
\item{In order to rank the found services ({\ExecutionTarget}s) the
  {\Broker} needs detailed knowledge about the job requirements, thus
  the {\JobDescription} is passed as input to the brokering process.}
\item{The {\Broker} filters and ranks the {\ExecutionTarget}s according 
  to the ranking method chosen by the user.}
\item{Each {\ExecutionTarget} has a method to return a specialized
  {\Submitter} which is capable of submitting jobs to the service it
  represents. The best suitable {\ExecutionTarget} for the job is
  asked to return a {\Submitter} for job submission.}
\item{The {\Submitter} takes the {\JobDescription} as input and
  uploads it to the computing service.}
\item{The {\Submitter} identifies local input files from the
  {\JobDescription} and uploads them to the computing service.}
\end{enumerate}

@@

Once a job is submitted job related information (job identification
string, cluster etc) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

\begin{enumerate}
\item{The {\JobSupervisor} takes four arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second is a list of strings containing job identifiers and job
  names, the third is a list of strings of clusters to select or
  reject (in the same format as described for the {\TargetGenerator}
  above). The last argument is the name of the file containing the
  local information about active jobs, hereafter called the joblist
  file.}
\item{A job identifier does not uniquely define which grid flavour
  runs a certain job. Thus this information is stored in the joblist
  file upon submission by the {\Submitter} and the joblist file is
  extensively used by the {\JobSupervisor} to identify the
  {\JobController} flavours which are to be loaded. The information in
  the joblist file is also used to look up the job identifier for jobs
  specified using job names. Alias resolving for the selected and
  rejected clusters are performed using the information in the
  {\UserConfig} object.}
\item{Suitable {\JobController}s are loaded}
\item{The list of job identifiers and selected and rejected clusters
  are passed to each {\JobController} which uses the information to
  fill its internal \texttt{JobStore}.}
\item{Residing within the {\JobSupervisor} the {\JobController}s are
  now accessible for external calls (i.e. job handling).}
\end{enumerate}

@@

In this section an overview of all important classes in the new
{\libarcclient} is given. The overview is subdivided in two parts where
first all the generic classes are presented,
Section~\ref{sec:genclass}, before the grid flavour specializations
are presented in Section~\ref{sec:plugins}. Classes are described both
in words and by code.

@@

The {\ExecutionTarget} is the class representation of a computing
resource (queue) capable of executing a grid job. It serves as input
to the {\Broker} which is able to filter and rank different 
{\ExecutionTarget}s from different grid flavours without a
priori knowing their difference. The {\ExecutionTarget} class mimics
the Glue2 information model (with a flattened structure), and thus a
mapping between attributes from other information systems into the
Glue2 format is needed. Appendix \ref{app:ExTarget} shows the current
mapping for the production ARC, ARC1 and gLite middlewares.

@@

Following a broker ranking jobs are to be submitted. Since all
information about the selected computing service resides within the
selected {\ExecutionTarget}, the {\ExecutionTarget} is capable of
returning a {\Submitter} capable of submitting a job to the service it
represents.

@@

The {\Broker} inherits from the {\ACC} base class in order to be loadable by the ARC \texttt{Loader}. It is the base class of the 
specialized {\Broker} and it implements the method for reducing a list of resources found by resource discovery (the list of 
{\ExecutionTarget}s residing witin the {\TargetGenerator}) to a list of resources capable of running a certain job:

\begin{shaded}
\begin{verbatim}
void PreFilterTargets(Arc::TargetGenerator& targen, Arc::JobDescription jd);
\end{verbatim}
\end{shaded}

The {\texttt PreFilterTargets} method compares every hardware and software requirement given in the job description against the 
computing resource (cluster) specifications stored in the {\ExecutionTarget}. If the{\ExecutionTarget} doesn't fulfill 
the requirements imposed by the job description, or it is impossible to carry out the matchmaking due to incomplete information 
published by the computing resource, the {\ExecutionTarget} will be removed from the list of possible targets. A detailed overview 
of the matchmaking between {\JobDescription} and {\ExecutionTarget} attributes is given in Appendix~\ref{sec:broker-mapping}.

Once prefiltered the remaining {\ExecutionTarget}s should be ranked in order to return the ``best'' {\ExecutionTarget} for 
job submission. Different ranking methods are implemented by the specialized brokers, but for usability and consistency reasons 
these methods are encapsulated by the {\Broker} base class method

\begin{shaded}
\begin{verbatim}
ExecutionTarget& GetBestTarget(bool &EndOfList);
\end{verbatim}
\end{shaded}

which invokes the {\texttt SortTargets} method implemented by the specialized broker (see Section~\ref{sec:brokerplugins}) 
and returns the best target. The {\texttt GetBestTarget} method is ``incremented'' at each call, thus upon a second call 
the second best {\ExecutionTarget} will be returned.

@@

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\libarcclient} library this functionality is implemented in the
{\JobDescription} class which parses job descriptions given in the 
XRSL~\cite{xrsl}, JDL~\cite{jdl} or JSDL~\cite{jsdl} formats into an 
internal representation based upon the upcoming PGI-JSDL proposal.

@@

The identification of the source description format is internally handled by a 
\texttt{JobDescriptionOrderer} class which identifies the format by pattern matching.
Once the format is determined from the elements are mapped from the original format (XRSL, JDL or JSDL) 
into the internal representation (the \texttt{JobInnerRepresentation} class). Mapping details 
are given in Section~\ref{sec:jobinnerrepresentation}.

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern matching
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and translation (if needed) of the job descriptions.

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} funcion as shown below:

@@

If the inner representation is empty or the source job descrition is not
valid, then the {\texttt GetProduct} output is empty too and the method 
returns with false. When the product format is the same as the source format 
and not XRSL, than the product string is set to the source string. The XRSL 
output is always generated from the inner representation, as it includes 
automatic job description modifications similar to those of the production 
ARC client. If the product format differs from the source format the 
{\texttt GetProduct} method calls upon the \texttt{JobDescriptionOrderer} 
class to carry out the translation.

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data is available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these events the {\texttt GetProduct} 
method returns with a false and an empty product stringt. For limitations in the translation
see Section~\ref{sec:jobinnerrepresentation}.

@@

The {\Job} is a generic job class for storing all job related
information. Attributes are derived from the Glue2 information model
and thus a mapping is needed for non Glue2 compliant grid middlewares.
Appendix~\ref{app:job} shows the present mapping schema.

@@

The gLite computing element offers several interfaces, one of them
being the Web Service based computing element interface known as the
CREAM CE~\cite{cream}. The current revision of this interface (CREAM
version 2) has been chosen for implementation within {\libarcclient} for the
following reasons:

@@

\subsection{Broker plugins}
\label{sec:brokerplugins}

\subsubsection{\RandomBroker}

The {\RandomBroker} ranks the {\ExecutionTarget}s randomly.

\subsubsection{\FastestCPUBroker}

The {\FastestCPUBroker} ranks the {\ExecutionTarget}s according to their CPU performance. The most 
reliable comparison is achieved through the usage of a benchmark scenario, and the {\FastestCPUBroker}
uses the CINT2000 (Integer Component of SPEC CPU2000)\footnote{http://www.spec.org/cpu2000/CINT2000/} 
benchmark for this purpose.

The {\texttt SortTargets} method has two steps:

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing the specint2000 benchmark information are removed from the list 
  of possible targets as their performance is unknown.}
\item{The {\ExecutionTarget}s are ranked such that the {\ExecutionTarget} with highest specint2000 value 
  receives top ranking}
\end{enumerate}

\subsubsection{\FastestQueueBroker}

The {\FastestQueueBroker} ranks the {\ExecutionTarget}s according to their queue length measured in percentage 
of the {\ExecutionTarget}'s size (i.e. the queue length divided by the number of total slots/CPUs). If more 
than one {\ExecutionTarget} has zero queue, the {\FastestQueueBroker} makes use of a basic load balancing method 
to rearrange the zero queue {\ExecutionTarget}s depending on their number of free slots/CPUs.

The {\texttt SortTargets} method has three steps:

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked top.}
\item{If more than one {\ExecutionTarget} has zero queue the targets are randomly reshuffled based upon how many free slots 
they have. E.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% propability of becoming the top ranked cluster.}
\end{enumerate}

\subsubsection{\DataBroker}

The {\DataBroker} ranks the {\ExecutionTarget}s according to how many megabytes of the requested input files that already 
stored in the cache of the computing resource the {\ExecutionTarget} represents. The broker is motivated by that jobs should 
be submitted to {\ExecutionTarget}s where the data already is, thus reducing the network load on both the computing resource 
and client side. The ranking method is based upon the A-REX\footnote{http://www.knowarc.eu/download/D1.2-3\_documentation.pdf} 
interface {\texttt CacheCheck} for querying for the presence of the file in the cache directory. This interface has a limitation 
in the current implementation as it can only use cache directory of format

@@

If the cachedir parameter involves {\%}U or other substitute element then the {\texttt CacheCheck} will not work.

The {\texttt SortTargets} method has four steps:

\begin{enumerate}
\item{Only the A-REX service has {\texttt CacheCheck} method, thus {\ExecutionTarget}s not running A-REX are removed.
therefore the other clusters will be ignored.}
\item{Information about input files is collected from the JobInnerRepresentation.}
\item{Each {\ExecutionTarget} is queried (through the {\texttt CacheCheck} method) for the existence of input files. 
A single query is used for achieving all the necessary information and file sizes are summarized. If there is problems 
determining file sizes, then the summarized size will be zero.}
\item{The possible {\ExecutionTarget}s are ranked in a descending order according to the amount of input data they have in cache.}
\end{enumerate}

Example of a CacheCheck request that can be sent to an A-REX service:

@@

Example CacheCheck response from the A-REX service:

@@

\subsubsection{\PythonBroker}

This {\PythonBroker} allows users to write their customized broker in
python. To use this broker the user should write a python class which 
should contain:

@@

The {\Config}, {\ExecutionTarget} and {\texttt JobInnerRepresentation} classes are
available in the swig generated arc python module.

To invoke the {\PythonBroker}, the name of the python module defining
the broker class and the name of the broker class must be given. If
e.g. the broker class MyBroker is defined in the python module
SampleBroker the command line option to arcsub to use this broker is:

@@

Given all components listed above it is possible to write versatile
command line interfaces (cli) for grid job submission and
management. {\libarcclient} offers the following native commands:

@@

http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/client/ExecutionTargetMapping.html

\chapter{Broker mapping}
\label{app:broker-mapping}
